Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-12-03 longSC.tex
model name

\section{Model Comparisons}
\label{sec:theory}
\subsection{Theoretical models}
\label{sec:models}
%We have used various models in this article. The {\sc HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency as a function of transverse momentum. 
%Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry). 
%We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}. 
We have compared the centrality dependence of our observables with theoretical model from~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}. The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$. Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions. 
%\textbf{Need a short description of event-by-event viscous hydrodynamic calculations from VISH2+1}.

@@

\subsection{Low Order Harmonic Correlations}
SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
The hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}. 
It has been demonstrated that NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
However, the sign of NSC(3,2) is positive in the models in 0-10\% central collisions while it is negative in data.
In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime. This observation helps to understand better the fluctuations in initial energy density.
NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe neither the centrality dependence nor the absolute values. This observed distinct discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions used to model the initial stages of heavy-ion collision need to be revisited to further constrain the $\eta/s(T)$, considering the difficulties in separating the role of the $\eta/s$  from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
The use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints on the detailed modeling of fluctuating initial conditions. The better constraints on the initial state conditions will certainly reduce the uncertainties of determining $\eta/s(T)$.

@@

\subsection{Higher Order Harmonic Correlations}
The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical calculations. 
The hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}. 
\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{Niemi:2015qia}, figure will be replaced later, just a place holder]}}

@@

\section{Summary}
\label{sec:summary}
In this article, we report the centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations.
The results are obtained by the Symmetric 2-harmonic 4-particle Cumulants (SC). It was demonstrated earlier in \cite{ALICE:2016kpq} that this method is insensitive to the non-flow effects and free from symmetry plane correlations.
We have found that fluctuations of $v_2$-$v_3$ and $v_3$-$v_4$ are anti-correlated in all centralities while fluctuations of $v_2$-$v_4$, $v_2$-$v_5$ and $v_3$-$v_5$ are correlated for all centralities. 
This measurement were compared to various hydrodynamic model calculations with different initial conditions as well as different parameterizations of the temperature dependence of $\eta/s$.
It is found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties. Therefore they have discriminating power in separating the effects of $\eta/s$  from the initial conditions to the final state particle anisotropies.
The sign of $v_3$-$v_2$ correlation in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations.
In the most central collisions the anisotropies originate mainly from fluctuations, where the initial ellipsoidal geometry which is dominating in mid-central collisions plays little role. This observation might help to understand the details of the fluctuations in initial conditions. 
The comparisons to VISH2+1 calculation show that all the models with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of higher order correlations, more clearly than lower order harmonic correlations. 
Based on the tested model parameters, the $\eta/s$ should be small and AMPT initial condition is favored by the data. A quite clear separation of the correlation strength between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
The default configuration of AMPT model describes well the normalized symmetric cumulants (NSC($m$,$n$)) for most of centralities and for most combinations of harmonics which were considered. Together with the measurements of individual harmonics these results provide further constraints on the system properties and help discriminating between theoretical models.
Finally, we have found that $v_3$ and $v_2$, $v_4$ and $v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions. This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out.
The results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.

>>>>

\section{Model Comparisons}
\label{sec:theory}
\subsection{Theoretical models}
\label{sec:models}
%We have used various models in this article. The {\sc HIJING} model~\cite{Wang:1991hta,Gyulassy:1994ew} was utilized to obtain the $p_{\rm T}$-weights~\cite{Bilandzic:2013kga} which were used to estimate systematic bias due to non-uniform reconstruction efficiency as a function of transverse momentum. 
%Secondly, the HIJING model was used to estimate the strength of non-flow correlations (typically few-particle correlations insensitive to the collision geometry). 
%We have evaluated the observables of interest in coordinate space by modeling the initial conditions with a MC-Glauber model~\cite{Miller:2007ri}. 
We have compared the centrality dependence of our observables with the EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia}, where the initial energy density profiles are calculated using a next-to-leading order perturbative-QCD+saturation model~\cite{Paatelainen:2012at,Paatelainen:2013eea}. The subsequent spacetime evolution is described by relativistic dissipative fluid dynamics with different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$. Each of the $\eta/s(T)$ parameterizations is adjusted to reproduce the measured $v_n$ from central to mid-peripheral collisions. 
%\textbf{Need a short description of event-by-event viscous hydrodynamic calculations from VISH2+1}.

@@

\subsection{Low Order Harmonic Correlations}
SC(3,2) and SC(4,2) are compared to several theoretical calculations. 
The EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown in Fig.~2 of Ref.~\cite{ALICE:2016kpq}. 
It has been demonstrated that NSC(3,2) observable is sensitive mainly to the initial conditions, while NSC(4,2) observable is sensitive to both the initial conditions and the system properties, which is consistent with the predictions from~\cite{Niemi:2012aj}.
However, the sign of NSC(3,2) is positive in the models in 0-10\% central collisions while it is negative in data.
In the most central collisions the anisotropies originate mainly from fluctuations, i.e.\ the initial ellipsoidal geometry characteristic for mid-central collisions plays little role in this regime. This observation helps to understand better the fluctuations in initial energy density.
NSC(4,2) observable shows better sensitivity for different $\eta/s(T)$ parameterizations but the model cannot describe neither the centrality dependence nor the absolute values. This observed distinct discrepancy between data and theoretical predictions indicates that the current understanding of initial conditions used to model the initial stages of heavy-ion collision need to be revisited to further constrain the $\eta/s(T)$, considering the difficulties in separating the role of the $\eta/s$  from the initial conditions to the final state particle anisotropies~\cite{Romatschke:2007mq,Shen:2011zc}.
The use of SC$(m,n)$ and NSC$(m,n)$ can provide new constraints on the detailed modeling of fluctuating initial conditions. The better constraints on the initial state conditions will certainly reduce the uncertainties of determining $\eta/s(T)$.

@@

\subsection{Higher Order Harmonic Correlations}
The higher order harmonic correlations (SC(4,3), SC(5,2) and SC(5,3)) are compared to several theoretical calculations. 
The EKRT+viscous hydrodynamic predictions with the different parameterizations for the temperature dependence of the shear viscosity to entropy density ratio $\eta/s(T)$ are shown on the left in Fig.~\ref{fig:Figure_5}. 
\noindent\textbf{\textcolor{blue}{[Waiting for $\eta/s(T)$ hydro calculations from Harri Niemi et. al~\cite{Niemi:2015qia}, figure will be replaced later, just a place holder]}}

@@

\section{Summary}
\label{sec:summary}
In this article, we report the centrality dependence of correlation between the higher order harmonics ($v_3$, $v_4$, $v_5$) and the lower order harmonics ($v_2$, $v_3$) as well as the transverse momentum dependence of $v_3$-$v_2$ and $v_4$-$v_2$ correlations.
The results are obtained by the Symmetric 2-harmonic 4-particle Cumulants (SC). It was demonstrated earlier in \cite{ALICE:2016kpq} that this method is insensitive to the non-flow effects and free from symmetry plane correlations.
We have found that fluctuations of $v_3$-$v_2$ and $v_4$-$v_3$ are anti-correlated in all centralities while fluctuations of $v_4$-$v_2$, $v_5$-$v_2$ and $v_5$-$v_3$ are correlated for all centralities. 
This measurement were compared to various hydrodynamic model calculations with different initial conditions as well as different parameterizations of the temperature dependence of $\eta/s$.
It is found that the different order harmonic correlations have different sensitivities to the initial conditions and the system properties. Therefore they have discriminating power in separating the effects of $\eta/s$  from the initial conditions to the final state particle anisotropies.
The sign of $v_3$-$v_2$ correlation in 0-10\% central collisions was found to be different between the data and hydrodynamic model calculations.
In the most central collisions the anisotropies originate mainly from fluctuations, where the initial ellipsoidal geometry which is dominating in mid-central collisions plays little role. This observation might help to understand the details of the fluctuations in initial conditions. 
The comparisons to VISH2+1 calculation show that all the models with large $\eta/s$ regardless of the initial conditions failed to capture the centrality dependence of higher order correlations, more clearly than lower order harmonic correlations. 
Based on the tested model parameters, the $\eta/s$ should be small and AMPT initial condition is favored by the data. A quite clear separation of the correlation strength between different initial conditions is observed for these higher order harmonic correlations compared to the lower order harmonic correlations.
The default configuration of AMPT model describes well the normalized symmetric cumulants (NSC($m$,$n$)) for most of centralities and for most combinations of harmonics which were considered. Together with the measurements of individual harmonics these results provide further constraints on the system properties and help discriminating between theoretical models.
Finally, we have found that $v_3$ and $v_2$, $v_4$ and $v_2$ correlations have moderate $p_{\rm T}$ dependence in mid-central collisions. This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out.
The results presented in this article can be used to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions.
